%\chapter{Control System for Complete Complex Autonomous Systems: Hubo-Ach}\label{sec:hubo-ach}
%\chapter{Thesis: Hubo-Ach - A Control System for Complete Complex Autonomous Systems}\label{sec:hubo-ach}
%\chapter{Hubo-Ach: Control System for Complete Complex Autonomous Systems}\label{sec:hubo-ach}
\chapter{Hubo-Ach: A Unified Algorithmic Framework for High DOF Robots}\label{sec:hubo-ach}


This section describes in detain the \textit{unified algorithmic framework for high degree of freedom complex systems and humanoid robots}.
An overview of the system is given in Section~\ref{sec:ach:overview}.
Timing and system testing is given in Section~\ref{sec:timing}
Validation examples are given in Section~\ref{sec:simpleExamples}, \ref{sec:hubo-ach-kinimatics} and \ref{sec:valve}.
Verification of Hubo-Ach from independent parties is given in Section~\ref{sec:hubo-achVerification} and results from surveys about the system is given in Section~\ref{sec:hubo-achSurvey}.


%% Hubo-Ach Inspiration
\section{Overview}\label{sec:ach:overview}

%% Hubo-Ach explanation
%% workign wth ros and other software that exists, why in C


\input{hubo-ach/hubo-ach-intro.tex}
\section{Inter Process Comunication Comparision}\label{sec:ipc}
	\input{hubo-ach/hubo-ach-ipc-comp.tex}
\section{Timing}\label{sec:timing}
	\input{hubo-ach/hubo-ach-timing.tex}
\section{CPU Usage}
	\input{hubo-ach/hubo-ach-cpu.tex}
\section{Verification Experiments}\label{sec:simpleExamples}
This section contains step by step verification examples showing the controller for high DOF complex system functions properly with the hubo system.
All controllers are implemented using the multiple processes approach and includes all latencies found in Section~\ref{sec:timing}.

	\subsection{Joint Space Step Response}\label{sec:singlejointStep}
		\input{examples/example-singlejontStep.tex}
	\subsection{Joint Space Step Response with Position Filtering}\label{sec:singlejointFilter}
		\input{examples/example-singlejontFilter.tex}
	\subsection{Compliance Amplification}\label{sec:singlejointRefComplience}
		\input{examples/example-singlejontComplience.tex}
	\subsection{Joint Space Step Response with Feedback Filtering}\label{sec:singlejointEnc}
		\input{examples/example-singlejontEnc.tex}

\section{Kinematics}\label{sec:hubo-ach-kinimatics}
Kinematic planning is a key focus of the Hubo-Ach controller.
This section provides two published examples of the Hubo-Ach controller being used for inverse kinematics and control.
Section~\ref{sec:valve} shows the work of Lofaro et. al. \cite{lofaroTePRA2013Valve} using Constrained Bi-Directional Rapidly-exploring Random Tree (CBiRRT) to provide a statically stable joint space trajectory allowing the robot to turn a valve.
Section~\ref{sec:6dofik} shows the work of Lofaro et. al. \cite{lofaroTePRA2013HuboAch} using traditional 6 DOF forward and inverse kinematic techniques to provide an analytical IK solution to each of the 6 DOF end effectors.
The additional use of on-line trapezoidal velocity profiling methods in Section~\ref{sec:trap} allow for the creation of a real-time IK controller based in Hubo-Ach.


\subsection{Valve Turning}\label{sec:valve}
	\input{examples/example-valveturning.tex}



\section{Six Degree of Freedom Inverse Kinematic Implementation Example}\label{sec:6dofik}
This section shows how we calculate the inverse kinematics (IK) for the Hubo's right arm and how we use that calculation in conjunction with Section~\ref{sec:simpleExamples}.  The result is the ability to command the end effector (EEF)

\input{examples/example-6dofIKsolutionIntro.tex}
	\subsection{Froward Kinematics} 
		\input{examples/example-6dofFKsolution.tex}
	\subsection{Inverse Kinematics}\label{sec:ik}
			\input{examples/example-6dofIKsolution.tex}

\section{Verification: Door Opening}\label{sec:hubo-achVerification}
	\input{examples/hubo-ach-door-open.tex}

\section{Validation: Peer Survey on Hubo-Ach}\label{sec:hubo-achSurvey}
	This section shows the peer survey taken by users of Hubo-Ach.
	Thirteen independent users were surveyed.
	The overwhelming conclusion was that the system is useful, was the unifying algorithmic framework as advertised and helped with development.
	Out of a score from 0-10 on the question \textit{"Would you use Hubo-Ach again the the future when programming Hubo"} received an average of 9.23 (see Table~\ref{table:q6}.
	Table~\ref{table:q1}, \ref{table:q2}, \ref{table:q3}, \ref{table:q4}, \ref{table:q5}, \ref{table:q6}

	\input{survey/q1t.tex}
	\input{survey/q2t.tex}
	\input{survey/q3t.tex}
	\input{survey/q4t.tex}
	\input{survey/q5t.tex}
	\input{survey/q6t.tex}

In conclusion Hubo-Ach is validated as being a useful \textit{unified algorithmic framework for complex systems and humanoid robots} by peers.
Shown to have consistent system performance in Section~\ref{sec:timing}.
It is verified via implementation of full body kinematic examples in Section~\ref{sec:valve} and \ref{sec:6dofik}.








