\chapter{Methodology}
%% Intro to methodology


%% --------- Balancing ----------
\section{Balancing}\label{sec:sec:balance}
	\input{pitch/balancing.tex}




%% ------------ Thorwing ---------------
\section{Throwing}\label{sec:baseball}
	\input{pitch/introduction.tex}
	
	\subsection{Throwing Using Sparse Reachable Map}\label{sec:sec:srm}
		\input{pitch/srm.tex}

	\subsection{Human to Humanoid Kinematic Mapping}\label{sec:sec:mocap}
		\input{pitch/mocap.tex}

	\subsection{Key-Frame Motion}\label{sec:sec:keyframe}
		\input{pitch/keyframe.tex}

%% --------- SRM - make sure they know this is what I did
\section{Sparse Reachable Map Velocity Space Inverse Kinematics}\label{sec:srm}
		%\input{srm/abstract.tex}
		%\input{srm/introduction.tex}
		\input{srm/priorwork.tex}
		\input{srm/methodology.tex}
		%% split trapozoidal motion profile into another section example


\section{Final Design}\label{sec:finalDesign}
	\input{pitch/finalDesign.tex}

\section{Conclusion}\label{sec:throw:conclusion}
	Throwing using the key-frame based method was the most reliable and successful.  
	The system was open-loop in respect to the location where it would throw the ball.
	This is why it over threw the ball during the real pitch, see Fig.~\ref{fig:hubo-throw-test}.
	The lessons learned when performing the throwing task is that
	\begin{enumerate}
		\item A unified algorithmic framework is needed for three tier testing
		\item Using such a framework the loop has to be closed on the ball's final location
		\item System for having a stable landing when taking a step
	\end{enumerate}

	Section~\ref{sec:hubo-ach} describes the unified framework that answer \#1 above.
	As stated before throwing is a full body locomotive task. 
	Section~\ref{sec:visuralServoing} closes the loop using visual methods.
	This shows how the unified algorithmic architecture can be used for visual servoing a full body locomotive tasks.
	This visual servoing example answer \#2 above.
	The use of active damping as seen in Section~\ref{sec:activedamping} allows the robot to land on the ground.
	This answers \#3 above.



		
